---
title: "Main figures for Cholera serosurveillance in partially vaccinated populations"
author: "Forrest Jones"
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: no
  word_document: default 
---

```{r setup, include=FALSE}


library(knitr)

knitr::opts_chunk$set(echo = FALSE,message = FALSE,warning = FALSE,
                      cache = TRUE,
                      fig.height = 7,
                      fig.width = 10, eval=FALSE,
                      dev="pdf" )

```





```{r load, eval = TRUE}

source("code/R/packages.R")
source("code/R/utils.R")
source("code/R/load-data.R")


```


## Table 1:Individual characteristics of culture confirmed cholera patients and vaccinated individuals
Serological data were also available for three uninfected household contacts of Bangladeshi cases enrolled with measurements taken at 2, 7, and 30 days after enrollment of the initial case


```{r eval=TRUE}


tab1_df <- final_df %>%
        filter(status %in% c("Case","Vaccinee")) %>%
        filter(studycode %in% c("SMIC","PIC","RB","IMS","RB","RIKS2")) %>%
        distinct(cohort,studycode,id,age_group,sex,blood,culture,status) %>%
# get categorical variables together
        group_by(cohort) %>%
        summarize(n=n(),
                  `< 5 years`=sum(age_group=="<5 years"),
                  `5-9 years`=sum(age_group=="5-9 years"),
                  `10-17 years`=sum(age_group=="10-17 years"),
                  `18+ years`=sum(age_group=="18+ years"),
                  
                  Female = sum(sex=="female"),
                  
                  `O Blood Group` = sum(blood=="O"),
                  
                  `V. cholerae O1 Ogawa isolated` = sum(culture=="O1-Ogawa"),
        ) %>%
        gather(variable,value,-c(cohort,n)) %>% 
        # filter(!is.na(value)) %>%
        mutate(percent=round(value/n*100)) %>%
        mutate(final_value= ifelse(is.na(value),"-",paste0(value," (",percent,")"))) %>%
        mutate(row_name=paste(variable,"(%)")) %>%
        select(cohort,n,row_name,final_value)


tab1_df %>%
        mutate(row_name=factor(row_name,
                               levels = c("< 5 years (%)",                     "5-9 years (%)"  ,                  
                                          "10-17 years (%)"   ,                "18+ years (%)"     ,               
                                          "Female (%)"  ,                      "O Blood Group (%)" ,               
                                          "V. cholerae O1 Ogawa isolated (%)")
        )) %>%
        mutate(column_header= case_when(
                cohort == "SMIC/PIC" ~ "Bangladeshi cholera cases",
                cohort == "BGD Vaccinee" ~ "Bangladeshi vaccinees",
                cohort == "HTI Vaccinee" ~ "Haitian vaccinees"
                
        )) %>%
        mutate(column_header=paste0(column_header,"\n(n=",n,")")) %>%
        select(column_header,row_name,final_value) %>%
        spread(column_header,final_value) %>%
        bind_rows(data.frame(row_name="Age Group"),.) %>%
        rename(Characteristics=row_name) %>%
        flextable::flextable() %>%
        flextable::autofit() %>%
        flextable::padding(i=2:5, j=1, padding.left=20) %>%
        flextable::align(align = "center",j=2:4,part="all") %>%
        flextable::width(width = 1.5) 


```


\pagebreak

## Figure 1: Multiplex bead assay measurements of IgG, IgM, and IgA against V. cholerae O1 antigens among vaccinated participants 

Y-axis indicates the log (base 10) of the relative antibody units (RAU) with limits at 10^-2 and 10-5. X-axis is in days and is square-root transformed. Each colored line indicates individual trajectories over time. The solid lines are Loess smooth functions. Rug plots show measurements from confirmed cases and uninfected household contacts classified within a 180-day infection window (black) and outside a 180-day infection window (purple).

```{r f1-spaghetti-rau,  eval=TRUE, fig.height = 7, fig.width = 10}

#data for figure 1
fig1_df <- final_df %>% 
        filter(antigen_pretty %in% c("Ogawa OSP","Inaba OSP","O139 OSP","CT-B","TcpA")) %>%
        mutate(antigen_pretty=factor(antigen_pretty,levels=c("Ogawa OSP","Inaba OSP","O139 OSP","CT-B","TcpA"))) %>%
        mutate(isotype=factor(isotype,levels=c("IgG","IgA","IgM"))) %>%
        filter(study_code!="R1")



#case true positives
true_pos <- fig1_df %>% filter(
                   status=="Case",
                   day > 2,
                   day<200
                   )

#case true negatives
true_neg <- fig1_df %>%
                filter(cohort=="SMIC/PIC") %>%
                anti_join(true_pos)
        



fig1_df %>%
        filter(status=="Vaccinee")  %>%
        ggplot(aes(y=RAU_value))+
                geom_line(aes(group=id,
                              x=day,
                              col=Vaccinee
                              ),
                          alpha=0.3
                          )+
                geom_rug(data=true_pos,sides="l",col="red",alpha=0.3)+
                geom_rug(data=true_neg,sides="r",col="black",alpha=0.3)+
                facet_grid(isotype~antigen_pretty)+
                scale_color_manual(values = c("cyan","#003262","#FDB515")
                                   )+
                scale_x_continuous("Days since first dose",breaks=c(1,30,200,365) ,trans="sqrt")+
        geom_vline(xintercept = 14,lty=2)+
        ylab("log10(1/RAU)")+
        guides(color=guide_legend(override.aes=list(alpha=NA)))+
        theme_cowplot()+
        theme(legend.position = "bottom")
  
  

```


\pagebreak


### Figure 2: Misclassification of vaccinated individuals

```{r f2-misclassify}

# Misclassification.R provides predictions for misclassification of vaccinees
# source("code/R/misclassification.R")

misclassify_df2 <- read_rds("data/generated_data/misclassify_df2.rds")

misclassify_df2 %>%
        filter((str_detect(cohort,"BGD"))) %>%
        mutate(age_group=ifelse(age<10,"Bangladeshi <10 years","Bangladeshi 10+ years")) %>%
        group_by(day,age_group,end_window) %>%
        summarize(seropos=mean(spec95_seropos))%>%
        ggplot(aes(fill=factor(day),col=factor(day),
                   y=seropos,x=factor(as.numeric(end_window))))+
        geom_col(position = position_dodge2(0.1))+
        scale_fill_viridis_d("Days since first dose")+
        scale_color_viridis_d("Days since first dose")+
        facet_wrap(age_group~.)+
        theme_cowplot()+
        xlab("Infection Window (Days)")+
        scale_y_continuous("False Positivity Rate",limits=c(0,0.4))+
        geom_hline(yintercept = 0.05,lty=2)


# misclassify_df <- read_rds("data/generated_data/misclassify_df.rds")
# 
# misclassify_df %>%
#         filter((str_detect(cohort,"BGD"))) %>%
#         mutate(age_group=ifelse(age<10,"Bangladeshi <10 years","Bangladeshi 10+ years")) %>%
#         group_by(day,age_group) %>%
#         summarize(across(original_45day:original_300day,.fns=mean)) %>%
#         gather(model,seropos,-c(day,age_group)) %>%
#         mutate(end_window=str_extract(model,"[0-9]{2,3}")) %>%
#         ggplot(aes(fill=factor(day),col=factor(day),
#                    y=seropos,x=factor(as.numeric(end_window))))+
#         geom_col(position = position_dodge2(0.1))+
#         scale_fill_viridis_d("Days since first dose")+
#         scale_color_viridis_d("Days since first dose")+
#         facet_wrap(age_group~.)+
#         theme_cowplot()+
#         xlab("Infection Window (Days)")+
#         # scale_y_continuous("False Positivity Rate",limits=c(0,0.4))+
#         geom_hline(yintercept = 0.05,lty=2)


```





```{r misclassify, eval=FALSE,fig.height = 8, fig.width = 8}


#####  Fit RF models and make predictions -------------

fpr_fit_list <- list()
raw_df <- data.frame()

for(t in c(45,120,200,300)){
        # for(v in 1:length(var_list)){
                v <- 1        
                marks <- var_list[[v]]
                
                cat("Window: ",t, "Variables: ",names(var_list)[v],"\n")        
                
                
                # fit_data <- wide_analysis %>%
                #         addInfectionWindow(end_window=t)
                fit_data <- final_wide %>%
                        filter(cohort =="SMIC/PIC")%>% 
                        mutate(day_actual=day)%>%
                        addInfectionWindow(end_window=t) 
                
                missing <- rowSums(is.na(fit_data[var_list[[v]]])) >0
                  
                fit_data <- fit_data[!missing,]      
                
                outcome <- paste0("inf_",t)
                
                # 1. run 100 models to find a cutoff
                #keep 50% fit and 50% to test 
                cut_data <- data.frame()
                
                for(j in 1:100){
                        
                        n_ind <-unique(fit_data$id) %>% length() 
                        
                        #define who is in and who is out
                        outside <-sample(fit_data$id,round(n_ind*0.5),replace=FALSE)
                        outside_df <- filter(fit_data,id %in% outside)
                        inside_df  <- filter(fit_data,!id %in% outside)%>%
                                addInfectionWindow(end_window=t)
                        
                        
                        # inside_w = NULL
                        
                        # if(weighted){
                        inside_w <- inside_df %>%
                                getWeight(end_window = t)  %>%
                                pull(weight)
                                
                        # }
                        
                        #fit rf model
                        inside_fit <- ranger::ranger(formula=make_formula(paste0("inf_",t),
                                                                          var_list[[v]]),
                                                     data=inside_df,
                                                     num.trees = 500,
                                                     case.weights = inside_w,
                                                     replace=TRUE
                        )
                        
                        
                        #find the cutoff for each 
                        performance <- 
                                outside_df %>% addInfectionWindow(end_window=t) %>%
                                getPerf_ranger(inside_fit,paste0("inf_",t)#,
                                               # spec=train_spec_cutoff
                                )
                        cut <- distinct(performance$data,youden_cutoff,
                                        spec99_cutoff,
                                        spec95_cutoff,
                                        spec90_cutoff
                        )
                        cut_data <- bind_rows(cut_data,cut)
                }
                
                #find cutoffs
                median_cut <- cut_data %>%
                        summarize(n =n(),
                                  youden_cutoff=median(youden_cutoff),
                                  spec99_cutoff=median(spec99_cutoff),
                                  spec95_cutoff=median(spec95_cutoff),
                                  spec90_cutoff=median(spec90_cutoff)
                        )
                
                print(median_cut)
                
                # 2. fit the model, predict, and apply cutoff 
                #fit the model
                
                #set weights if needed
                # w= NULL
                # if(weighted){
                w <- fit_data%>%
                        getWeight(end_window = t)  %>%
                        pull(weight)
                        
                # }
                
                this_fit<- ranger::ranger(data=fit_data,
                                          formula=make_formula(outcome,var_list[[v]]),
                                          num.trees= tree_param,
                                          case.weights = w,
                                          replace = TRUE
                )
                
                #
                #calculate the individual's samples seropositivity
                # test_data <- vax_wide_RAU %>%
                #         addInfectionWindow(end_window=t)
                test_data <- final_wide %>%
                        filter(str_detect(cohort,"Vaccinee"))%>%
                        addInfectionWindow(end_window=t)
                
                test_missing <- rowSums(is.na(test_data[var_list[[v]]])) >0
                
                test_data <- test_data[!test_missing,]  
                        
                        
                test_data["truth"] <- test_data[outcome]
                out_preds <-predict(this_fit,
                                    test_data,
                                    predict.all=TRUE)
                
                #store the data
                fpr_df <- test_data %>%
                                              mutate(prediction=out_preds[[1]] %>% rowMeans()-1) %>%
                                              mutate(youden_cutoff=median_cut$youden_cutoff,
                                                     spec99_cutoff=median_cut$spec99_cutoff,
                                                     spec95_cutoff=median_cut$spec95_cutoff,
                                                     spec90_cutoff=median_cut$spec90_cutoff
                                              ) %>%
                                              mutate(
                                                      youden_seropos = ifelse(prediction>youden_cutoff,
                                                                              1,0
                                                      ),
                                                      spec99_seropos = ifelse(prediction>spec99_cutoff,
                                                                              1,0),
                                                      spec95_seropos = ifelse(prediction>spec95_cutoff,
                                                                              1,0),
                                                      spec90_seropos = ifelse(prediction>spec90_cutoff,
                                                                              1,0),
                                                      
                                              ) %>%
                        mutate(variables=names(var_list)[v]) %>%
                        mutate(end_window=as.character(t))
                
                out_tmp <- list(
                        cutoffs=cut_data,
                        train=fit_data,
                        fit=this_fit,
                        preds=fpr_df
                )
                
                fpr_fit_list[[as.character(t)]][[names(var_list)[v]]] <- out_tmp
                raw_df <- bind_rows(raw_df,fpr_df)
                
        # }
}

raw_df <- raw_df %>% mutate(variables=factor(variables,levels=names(var_list)))

write_rds(fpr_fit_list,
          paste0(path,"fpr_fit_list.rds")
)

write_rds(raw_df,
          paste0(path,"raw_df.rds")
)


```

```{r}
raw_df <- read_rds(
          paste0(path,"raw_df.rds")
)


```


```{r}

###check the misclassification

raw_df %>% 
        mutate(age_group=ifelse(age<10,"child","adult")) %>%
        group_by(end_window,day) %>%
        summarize(seropos=mean(spec95_seropos)) %>%
        ggplot(aes(x=day,y=seropos))+
        geom_col()+
        facet_wrap(.~end_window)



```

```{r eval=FALSE}
options(mc.cores = 1)


tvfpr_fit <- list()
tvfpr_df <- data.frame()

raw_df_list <- list(
        
        `Bangladeshi <10 years` = filter(raw_df, cohort=="BGD Vaccinee") %>%
                                        filter(age<10),
        `Bangladeshi 10+ years`= filter(raw_df, cohort=="BGD Vaccinee") %>%
                                        filter(age>=10),
        `Haitian 18+ years` = filter(raw_df, cohort=="HTI Vaccinee") ,
        
        `All Vaccinees` = raw_df

)

for(t in c(45,120,200,300)){
        for(dat in names(raw_df_list)){
                
        

                        
                        cat("Window: ",t, " Population: ",dat,"\n")  
                        
                        # estimate time-varying sensitivity
                        tvfpr_tmp <- fit_tvfpr(data = raw_df_list[[dat]] %>%
                                                       filter(end_window==t),
                                                  end_window=t,
                                                  seropos_type= "spec95_seropos",
                                                  last_time = 365,
                                                  curve="cubic"
                        )
                        
                        tvfpr_fit[[as.character(t)]][[dat]] <- tvfpr_tmp
                        
                        tmp_df<- tvfpr_tmp$summary_df 
                        
                        if(!is.null(tmp_df)){
                                tmp_df<- tmp_df %>%
                                        mutate(variables="Reduced IgG Panel")%>%
                                        mutate(seropos_type="spec95_seropos") %>%
                                        mutate(end_window=t) %>%
                                        mutate(population=dat)

                        }
                        
                        
                        tvfpr_df <-bind_rows(tvfpr_df,tmp_df)
                        
                        
                }}





write_rds(tvfpr_fit,
          paste0(path,"tvfpr_fit.rds")
)
write_rds(tvfpr_df,
          paste0(path,"tvfpr_df.rds")
)

```


```{r eval=FALSE}

path <- "source/final_code/vax_strategy/generated_rds/fpr-estimates/"


raw_df <- read_rds(
          paste0(path,"raw_df.rds")
)


tvfpr_df <- read_rds(
          paste0(path,"tvfpr_df.rds")
)


bgd_fpr<- raw_df %>% 
        filter((str_detect(cohort,"BGD"))) %>%
        mutate(age_group=ifelse(age<10,"Bangladeshi <10 years","Bangladeshi 10+ years")) %>%
        group_by(age_group,end_window,day) %>%
        summarize(seropos=mean(spec95_seropos)) %>%
        ggplot(aes(fill=factor(day),col=factor(day),
                   y=seropos,x=factor(as.numeric(end_window))))+
        geom_col(position = position_dodge2(0.1))+
        scale_fill_viridis_d("Days since first dose")+
        scale_color_viridis_d("Days since first dose")+
        facet_wrap(age_group~.)+
        theme_cowplot()+
        xlab("Infection Window (Days)")+
        scale_y_continuous("False Positivity Rate",limits=c(0,0.4))+
        geom_hline(yintercept = 0.05,lty=2)

cont_fpr <- tvfpr_df %>% 
        filter(!(str_detect(population,"Bangladesh"))) %>%
        ggplot(aes(x=time,y=median,col=factor(end_window),
                   fill=factor(end_window)
                   ))+
        geom_line()+
        geom_ribbon(aes(ymin=lb,ymax=ub),col=NA,
                                    alpha=0.5,
                        ) +
        facet_wrap(.~fct_rev(population))+
        xlab("Days since first dose")+
        scale_y_continuous("False Positivity Rate",limits=c(0,0.4))+
        scale_fill_brewer("Infection Window (Days)",palette = "Dark2")+
        scale_color_brewer("Infection Window (Days)",palette = "Dark2")+
        theme_cowplot()+
        geom_hline(yintercept = 0.05,lty=2)

plot_grid(bgd_fpr+theme(legend.position = "bottom"),
          cont_fpr+theme(legend.position = "bottom"),
          labels=c("A","B"),nrow=2)


```

\pagebreak

### Figure 3: Comparison of serological measurements among recently infected and recently vaccinated individuals. 
Boxplots show the distributions for each antibody measurement (A). Only a subset of Bangladeshi vaccinees had measurements for anti-O139 OSP IgA and IgM. The two dimensions of the separate multidimensional scaling analyses are shown in the scatterplot for each denoted time window (B). 

```{r compare, eval=FALSE,fig.height = 8, fig.width = 8}

generate_MDS <- function(data,regex_string="Ogawa|Inaba|TcpA|CtxB|IgG_O139"){
        
        mds_data <- data %>% 
                select(vaxinf_class,matches(regex_string))
                # select(vaxinf_class,matches("Ogawa|Inaba|TcpA|IgG_O139"))
        
        mds_dist = dist(x = scale(mds_data[,-1]))
        mds_analysis <- mds(delta = mds_dist , ndim = 2 , type = "ratio")
        
        out <- bind_cols(select(mds_data,vaxinf_class),
                              as.data.frame(mds_analysis$conf))
        
        return(out)
        
}


compare_data <- final_df %>%
        filter(status %in% c("Vaccinee","Case") ) %>%
        filter(study_code!="R1") %>%
        # filter(cohort %in% c("BGD Vaccinee","SMIC/PIC")) %>%
        #limit vaccinees to only baseline and "recent samples"
        # filter(!(status=="Vaccinee" & !(day>3  & day <45))) %>%
        mutate(vaxinf_class =case_when(
                status=="Case" & day > 3 & day<200 ~ "Recently Infected",
                status=="Vaccinee" & day> 3 & day<200 ~ "Recently Vaccinated",
                TRUE ~ "Neither"
        )) %>%
        left_join(antigen_df)  %>%
        filter(vaxinf_class!="Neither")


compare_data_wide<- compare_data %>%
        select(sample,id,vaxinf_class,isotype,antigen_pretty,marker,RAU_value,day,age,status) %>% 
                        select(-isotype,-antigen_pretty) %>%
                        # mutate(RAU_value=log10(1/RAU_value)) %>%
                        spread(marker,RAU_value) %>%
                        mutate(vaxinf_class=str_remove_all(vaxinf_class," |,")) %>%
                        mutate(vaxinf_class=factor(vaxinf_class))


boxplot <- compare_data %>% 
                filter(antigen_pretty %in% c("Ogawa OSP","CT-B","TcpA","Inaba OSP","O139 OSP"))%>%
                mutate(antigen_pretty=factor(antigen_pretty,
                                             levels=c("Ogawa OSP","Inaba OSP",
                                                      "O139 OSP", "CT-B", "TcpA")
                )) %>%
                mutate(isotype=factor(isotype,levels=c("IgG","IgA","IgM"))) %>%
                mutate(vaxinf_class=case_when(
                        vaxinf_class=="Recently Infected" ~ "Infected <200 days ago",
                        vaxinf_class=="Recently Vaccinated" ~ "Vaccinated <200 days ago"
                )) %>%
                ggplot(aes(x=antigen_pretty,y=RAU_value,col=vaxinf_class))+
                geom_boxplot()+
                facet_wrap(.~isotype,nrow=1)+
                theme_cowplot()+
                theme(#axis.text.x = element_text(angle=45,hjust=1),
                        legend.position="bottom"
                )+
                xlab("Antigen")+
                scale_color_manual("Class", values=c("red","darkblue"))+
                ylab("log10(1/RAU)")+
                theme(axis.text.x = element_text(angle=45,
                                                 hjust=1
                ))



mds_plot <- bind_rows(
        compare_data_wide %>% filter(day<=45) %>%
                generate_MDS() %>% mutate(time_window="<=45 days"),
        compare_data_wide %>% filter(day>45 & day<=120)%>%
                generate_MDS() %>% mutate(time_window="46-120 days"),
        compare_data_wide %>% filter(day>120 & day<=200)%>%
                generate_MDS() %>% mutate(time_window="121-200 days")
)%>%
        mutate(time_window=factor(time_window,
                                  levels=c("<=45 days",
                                           "46-120 days",
                                           "121-200 days"
                                           )
        )) %>%

        mutate(vaxinf_class=recode(vaxinf_class,
                                   "RecentlyInfected" ="Recently Infected",
                                   "RecentlyVaccinated"="Recently Vaccinated"
        )) %>%
                ggplot(aes(x=D1,y=D2,col=vaxinf_class)) +
                geom_point(alpha=0.5,shape=16)+
                scale_color_manual("Class", values=c("red","darkblue"))+
                xlab("Dimension 1")+
                ylab("Dimension 2")+
        facet_wrap(.~time_window,scales="free")+
        theme_cowplot()


plot_grid(boxplot,
          mds_plot+theme(legend.position="none"),
          nrow=2,
          labels=c("A","B"))

```

```{r}
compare_data <- final_df %>%
        filter(status %in% c("Vaccinee","Case") ) %>%
        filter(study_code!="R1") %>%
        # filter(cohort %in% c("BGD Vaccinee","SMIC/PIC")) %>%
        #limit vaccinees to only baseline and "recent samples"
        # filter(!(status=="Vaccinee" & !(day>3  & day <45))) %>%
        mutate(vaxinf_class =case_when(
                status=="Case" & day > 3 & day<200 ~ "Recently Infected",
                status=="Vaccinee" & day> 3 & day<200 ~ "Recently Vaccinated",
                TRUE ~ "Neither"
        )) %>%
        left_join(antigen_df)  %>%
        filter(vaxinf_class!="Neither")


compare_data_wide<- compare_data %>%
        select(sample,id,vaxinf_class,isotype,antigen_pretty,marker,RAU_value,day,age,status) %>% 
                        select(-isotype,-antigen_pretty) %>%
                        # mutate(RAU_value=log10(1/RAU_value)) %>%
                        spread(marker,RAU_value) %>%
                        mutate(vaxinf_class=str_remove_all(vaxinf_class," |,")) %>%
                        mutate(vaxinf_class=factor(vaxinf_class))


boxplot <- compare_data %>% 
                filter(antigen_pretty %in% c("Ogawa OSP","CT-B","TcpA","Inaba OSP","O139 OSP"))%>%
                mutate(antigen_pretty=factor(antigen_pretty,
                                             levels=c("Ogawa OSP","Inaba OSP",
                                                      "O139 OSP", "CT-B", "TcpA")
                )) %>%
                mutate(isotype=factor(isotype,levels=c("IgG","IgA","IgM"))) %>%
                mutate(vaxinf_class=case_when(
                        vaxinf_class=="Recently Infected" ~ "Infected <200 days ago",
                        vaxinf_class=="Recently Vaccinated" ~ "Vaccinated <200 days ago"
                )) %>%
                ggplot(aes(x=antigen_pretty,y=RAU_value,col=vaxinf_class))+
                geom_boxplot()+
                facet_wrap(.~isotype,nrow=1)+
                theme_cowplot()+
                theme(#axis.text.x = element_text(angle=45,hjust=1),
                        legend.position="bottom"
                )+
                xlab("Antigen")+
                scale_color_manual("Class", values=c("red","darkblue"))+
                ylab("log10(1/RAU)")+
                theme(axis.text.x = element_text(angle=45,
                                                 hjust=1
                ))



mds_plot <- bind_rows(
        compare_data_wide %>% filter(day<=45) %>%
                generate_MDS(regex_string="Ogawa|Inaba|TcpA|IgG_O139") %>% mutate(time_window="<=45 days"),
        compare_data_wide %>% filter(day>45 & day<=120)%>%
                generate_MDS(regex_string="Ogawa|Inaba|TcpA|IgG_O139") %>% mutate(time_window="46-120 days"),
        compare_data_wide %>% filter(day>120 & day<=200)%>%
                generate_MDS(regex_string="Ogawa|Inaba|TcpA|CtxB|IgG_O139") %>% mutate(time_window="121-200 days")
)%>%
        mutate(time_window=factor(time_window,
                                  levels=c("<=45 days",
                                           "46-120 days",
                                           "121-200 days"
                                           )
        )) %>%

        mutate(vaxinf_class=recode(vaxinf_class,
                                   "RecentlyInfected" ="Recently Infected",
                                   "RecentlyVaccinated"="Recently Vaccinated"
        )) %>%
                ggplot(aes(x=D1,y=D2,col=vaxinf_class)) +
                geom_point(alpha=0.5,shape=16)+
                scale_color_manual("Class", values=c("red","darkblue"))+
                xlab("Dimension 1")+
                ylab("Dimension 2")+
        facet_wrap(.~time_window,scales="free")+
        theme_cowplot()


plot_grid(boxplot,
          mds_plot+theme(legend.position="none"),
          nrow=2,
          labels=c("A","B"))


```


\pagebreak


### Figure 4 : Three class model

```{r}

### markers
three_var <- data.frame(marker=colnames(final_wide)) %>%
                filter(str_detect(marker,"CtxB|Ogawa|Inaba")) %>%
                filter(str_detect(marker,"IgG")) %>% 
                unlist() %>% unname()

all_var <- data.frame(marker=colnames(final_wide)) %>%
                filter(str_detect(marker,"CtxB|Ogawa|Inaba|TcpA|IgG_O139")) %>%
                unlist() %>% c("age") %>% unname()


final_wide_nomissing <- final_wide[rowSums(is.na(final_wide[all_var]))==0,]


bangladeshi_fitdata <- final_wide_nomissing %>%
                filter(cohort %in% c("SMIC/PIC","BGD Vaccinee")) %>%
                mutate(vaxinf_class =case_when(
                        status=="Case" & day > 3 & day<200 ~ "RecentlyInfected",
                        status=="Vaccinee" & day> 3 & day<200 ~ "RecentlyVaccinated",
                        TRUE ~ "Neither"
                ))  %>%
         mutate(vaxinf_class2 =case_when(
                        status=="Case" & day > 3 & day<200 ~ "RecentlyInfected",
                        TRUE ~ "Neither"
                ))  %>%
        mutate(rowIndex=1:nrow(.))


```



```{r loocv}

path <- "source/final_code/vax_strategy/generated_rds/vax-classification/loocv/"


formula_all <- make_formula("vaxinf_class",all_var)
fit_all <- runCaretLOOCV(formula_all, dat=bangladeshi_fitdata)
write_rds(fit_all, paste0(path,"fit_all.rds"))

# importance_all <- caret::varImp(fit_all,scale=FALSE)


formula_three <- make_formula("vaxinf_class",three_var)
fit_three <- runCaretLOOCV(formula_three, dat=bangladeshi_fitdata)
write_rds(fit_three,paste0(path,"fit_three.rds"))

# importance_three <- caret::varImp(fit_three,scale=FALSE)

```


```{r}

path <- "source/final_code/vax_strategy/generated_rds/vax-classification/loocv/"

fit_all <- read_rds(paste0(path,"fit_all.rds"))
fit_three <- read_rds(paste0(path,"fit_three.rds"))



fit_all$pred %>% select(obs,Neither,RecentlyInfected,RecentlyVaccinated,rowIndex) %>%
        gather(pred,proportion,-c(obs,rowIndex)) %>%
        left_join(bangladeshi_fitdata) %>%
        ggplot(aes(y=reorder(sample,day),x=proportion,fill=pred))+
        geom_col()+
        facet_wrap(obs~paste(cohort,status),scales = "free")+
        theme_cowplot()+
        scale_fill_brewer("Predicted Class",palette="Dark2")+
        xlab("Proportion of Trees")+
        ylab("Sample ID")

coverage <- 0.5

fit_all$pred %>% 
        group_by(pred,obs) %>%
        count() %>%
        group_by(obs)%>%
        mutate(prop=n/sum(n)) %>%
        arrange(obs) %>%
        filter(obs!="RecentlyInfected") %>%
        ungroup() %>%
        mutate(multi=coverage*prop) %>%
        group_by(pred) %>%
        summarize(prop=sum(multi))


fit_all$pred %>% select(obs,Neither,RecentlyInfected,RecentlyVaccinated,rowIndex,pred) %>%
        gather(class,proportion,-c(obs,rowIndex,pred)) %>%
        left_join(bangladeshi_fitdata) %>%
        ggplot(aes(x=day,y=proportion))+
        geom_line(aes(group=id),alpha=0.3)+
        geom_point(aes(col=obs))+
        facet_grid(class~paste(cohort,status),scales = "free")+
        theme_cowplot()+
        scale_color_brewer("Observed", palette="Dark2")+
        ylab("Proportion of Trees")



fit_all$pred %>% select(obs,Neither,RecentlyInfected,RecentlyVaccinated,rowIndex,pred) %>%
        gather(class,proportion,-c(obs,rowIndex,pred)) %>%
        left_join(bangladeshi_fitdata) %>%
        ggplot(aes(col=class,y=proportion,x=obs))+
        geom_boxplot()+
        facet_grid(.~paste(cohort,status),scales = "free",space = "free")+
        theme_cowplot()+
        scale_color_brewer("Predicted", palette="Dark2")+
        ylab("Proportion of Trees")+
        xlab("Observed")+
        coord_flip()

        


```


```{r external-validation}

formula_all <- make_formula("vaxinf_class",all_var)
formula_three <- make_formula("vaxinf_class",three_var)
formula_all2 <- make_formula("vaxinf_class2",all_var)
formula_three2 <- make_formula("vaxinf_class2",three_var)

ranger_all <- ranger::ranger(formula_all, bangladeshi_fitdata %>%
                                     mutate(vaxinf_class=factor(vaxinf_class))
                                     )
ranger_three <- ranger::ranger(formula_three, bangladeshi_fitdata %>%
                                     mutate(vaxinf_class=factor(vaxinf_class))
                                     )
ranger_all2 <- ranger::ranger(formula_all2, bangladeshi_fitdata %>%
                                     mutate(vaxinf_class2=factor(vaxinf_class2))
                                     )
ranger_three2 <- ranger::ranger(formula_three2, bangladeshi_fitdata %>%
                                     mutate(vaxinf_class2=factor(vaxinf_class2))
                                     )

test_data <-final_wide_nomissing %>%
                filter(cohort %in% c("HTI Vaccinee","ETEC Challenge")) %>%
                mutate(`Full Set 3-class`=predict(ranger_all,data=.)$predictions,
                       `Three Markers 3-class`=predict(ranger_three,.)$predictions,
                       `Full Set 2-class`=predict(ranger_all2,.)$predictions,
                       `Three Markers 2-class`=predict(ranger_three2,.)$predictions
                       ) 

test_data %>%
        select(cohort,day, `Full Set 3-class`, `Three Markers 3-class`, `Full Set 2-class`, `Three Markers 2-class`) %>%
        gather(model,prediction,-c(cohort,day)) %>%
        group_by(model,day) %>%
        summarize(FPR=mean(prediction=="RecentlyInfected")) %>%
        ggplot(aes(x=factor(day),y=FPR))+ geom_col(position = position_dodge2())+
        facet_wrap(.~model,nrow=1)+
        theme_cowplot()+
        theme(axis.text.x = element_text(angle=45,hjust=1))
```

```{r}

path <- "source/final_code/vax_strategy/generated_rds/vax-classification/loocv/"

fit_all <- read_rds(paste0(path,"fit_all.rds"))
fit_three <- read_rds(paste0(path,"fit_three.rds"))


prop_df <- bind_rows(
                bangladeshi_fitdata %>% 
                        mutate(rowIndex=1:n()) %>%
                        left_join(fit_all$pred) %>%
                        mutate(markers="Full Set"),
                bangladeshi_fitdata %>% 
                        mutate(rowIndex=1:n()) %>%
                        left_join(fit_three$pred) %>%
                        mutate(markers="Three Markers"),
)

roc_df <- prop_df %>%
        select(obs,RecentlyInfected,RecentlyVaccinated,markers)  %>%
        gather(Class,value,-c(obs,markers)) %>%
        mutate(truth=ifelse(obs==Class,1,0))




#show roc curves and variable importance
p4a <- roc_df %>%
        mutate(Class = str_replace(Class,"Recently","Recently ")) %>% 
        ggplot()+ 
        geom_roc(aes(m = value, d = truth,col=Class,lty=markers),labels=FALSE,n.cuts=0)+ 
        geom_abline(lty=3,col="grey50")+
        xlab("False Positivity Rate")+
        ylab("True Positivity Rate")+
        scale_color_manual("Markers",values=c("red","darkblue"))+
        theme_cowplot()+
        facet_wrap(.~Class)+
        theme(legend.position = "bottom")


# prop_df %>% filter(status=="Contact") %>%
#         group_by(markers) %>%
#         summarize(prop=mean(pred=="Neither"))

p4b <- prop_df %>% filter(status %in% c("Vaccinee","Case")) %>%
        group_by(markers,day,status) %>%
        summarize(`Recently Vaccinated`=mean(pred=="RecentlyVaccinated"),
                  `Recently Infected`=mean(pred=="RecentlyInfected")
                  ) %>%
        gather(Prediction,`Proportion Predicted`,-c(markers,day,status)) %>%
        ggplot(aes(x=day,y=`Proportion Predicted`))+
                geom_line(aes(lty=markers,col=Prediction))+
        scale_y_continuous(limits=c(0,1))+
        theme_cowplot()+
        facet_grid(.~status,scales="free_x")+
        scale_color_manual(values=c("red","darkblue"))+
        xlab("Days since exposure")+
        theme(legend.position = "none")
 


test_data <-final_wide_nomissing %>%
                filter(cohort %in% c("HTI Vaccinee","ETEC Challenge")) %>%
                mutate(`Full Set`=predict(fit_all,.),
                       `Three Markers`=predict(fit_three,.)
                       ) 


p4c <- test_data %>% filter(cohort=="HTI Vaccinee") %>%
        select(day,`Full Set`,`Three Markers`) %>%
        gather(Markers,prediction,-day) %>%
        group_by(day,Markers) %>%
        summarize(`Recently Vaccinated`=mean(prediction=="RecentlyVaccinated"),
                  `Recently Infected`=mean(prediction=="RecentlyInfected"),
                  ) %>%
        gather(category,proportion,-c(day,Markers)) %>%
        ggplot(aes(x=day,y=proportion))+
        geom_line(aes(col=category,lty=Markers))+
        theme_cowplot()+
        scale_y_continuous("Proportion Predicted",limits=c(0,1))+
        xlab("Days since vaccination")+
        scale_color_manual(values=c("red","darkblue"))+
        theme(legend.position = "none")




plot_grid(p4a,p4b, p4c,ncol=1,
          labels=c("A","B","C")
          )

# prop_df %>% filter(status=="Case") %>%
#         group_by(markers,day) %>%
#         summarize(prop=mean(pred=="RecentlyInfected")) %>%
#         ggplot(aes(x=day,y=prop))+
#                 geom_line(aes(lty=markers),col="red")+
#         scale_y_continuous(limits=c(0,1))+
#         scale_x_continuous(trans="sqrt")+
#         theme_bw()
        
        




```

```{r}

#confusion matrix

prop_df %>%
                group_by(pred,obs,markers) %>%
                count() %>%
                group_by(obs,markers) %>%
                mutate(prop=n/sum(n))%>%
                mutate(Predicted = str_replace(pred,"Recently","Recently\n")) %>%
                mutate(Observed = str_replace(obs,"Recently","Recently\n")) %>%
                ggplot(aes(x=Observed,y=Predicted))+
                        geom_tile(aes(fill=prop*100))+
                        # scale_fill_viridis_c("%",limits=c(0,100),direction = -1)+
                        scale_fill_distiller("%",
                                             palette = "Oranges",
                                             limits=c(0,100),direction = 1)+
                        geom_text(aes(label=scales::percent(prop,1)))+
                theme_cowplot()+
                theme(axis.text.x = element_text(angle=45,hjust=1))+
                facet_wrap(.~markers)



```

```{r}


test_data <-final_wide_nomissing %>%
                filter(cohort %in% c("HTI Vaccinee","ETEC Challenge")) %>%
                mutate(`Full Set`=predict(fit_all,.),
                       `Three Markers`=predict(fit_three,.)
                       ) 


test_data %>% filter(cohort=="HTI Vaccinee") %>%
        select(day,`Full Set`,`Three Markers`) %>%
        gather(Markers,prediction,-day) %>%
        group_by(day,Markers) %>%
        summarize(`Recently Vaccinated`=mean(prediction=="RecentlyVaccinated"),
                  `Recently Infected`=mean(prediction=="RecentlyInfected"),
                  `Neither`=mean(prediction=="Neither")
                  ) %>%
        gather(category,proportion,-c(day,Markers)) %>%
        mutate(category=factor(category,levels=c("Neither",
                                                 "Recently Vaccinated",
                                                 "Recently Infected"
                                                 ))) %>%
        ggplot(aes(x=factor(day),y=proportion))+
        geom_col(aes(fill=Markers),position=position_dodge())+
        facet_wrap(.~category)

test_data %>% filter(cohort=="HTI Vaccinee") %>%
        select(day,`Full Set`,`Three Markers`) %>%
        gather(Markers,prediction,-day) %>%
        group_by(day,Markers) %>%
        summarize(`Recently Vaccinated`=mean(prediction=="RecentlyVaccinated"),
                  `Recently Infected`=mean(prediction=="RecentlyInfected"),
                  `Neither`=mean(prediction=="Neither")
                  ) %>%
        gather(category,proportion,-c(day,Markers)) %>%
        mutate(category=factor(category,levels=c("Neither",
                                                 "Recently Vaccinated",
                                                 "Recently Infected"
                                                 ))) %>%
        ggplot(aes(x=factor(day),y=proportion))+
        geom_col(aes(fill=category))+
        facet_wrap(.~Markers)






```



## Two class model

```{r}

bangladeshi_twofitdata <- final_wide_nomissing %>%
                filter(cohort %in% c("SMIC/PIC","BGD Vaccinee")) %>%
                mutate(vaxinf_class =case_when(
                        status=="Case" & day > 3 & day<200 ~ "RecentlyInfected",
                        TRUE ~ "NotRecentlyInfected"
                )) 

two_formula_all <- make_formula("vaxinf_class",all_var)
two_fit_all <- runCaretLOOCV(formula_all, dat=bangladeshi_twofitdata)
two_importance_all <- caret::varImp(two_fit_all,scale=FALSE)


two_formula_three <- make_formula("vaxinf_class",three_var)
two_fit_three <- runCaretLOOCV(formula_three, dat=bangladeshi_twofitdata)
two_importance_three <- caret::varImp(two_fit_three,scale=FALSE)




two_prop_df <- bind_rows(
                bangladeshi_fitdata %>% 
                        mutate(rowIndex=1:n()) %>%
                        left_join(two_fit_all$pred) %>%
                        mutate(markers="Full Set"),
                bangladeshi_fitdata %>% 
                        mutate(rowIndex=1:n()) %>%
                        left_join(two_fit_three$pred) %>%
                        mutate(markers="Three Markers"),
)
        


two_roc_df <- two_prop_df %>%
        select(obs,RecentlyInfected,markers)  %>%
        gather(Class,value,-c(obs,markers)) %>%
        mutate(truth=ifelse(obs==Class,1,0))


two_roc_df %>%
        mutate(Class = str_replace(Class,"Recently","Recently ")) %>%
        ggplot()+ 
        geom_roc(aes(m = value, d = truth,col=Class,lty=markers),labels=FALSE,n.cuts=0)+ 
        geom_abline(lty=3,col="grey50")+
        xlab("False Positivity Rate")+
        ylab("True Positivity Rate")+
        scale_color_manual(values=c("red","darkblue"))+
        theme_cowplot()#+


        

two_prop_df %>%
                group_by(pred,obs,markers) %>%
                count() %>%
                group_by(obs,markers) %>%
                mutate(prop=n/sum(n))%>%
                mutate(Predicted = str_replace(pred,"Recently","Recently\n")) %>%
                mutate(Observed = str_replace(obs,"Recently","Recently\n")) %>%
                ggplot(aes(x=Observed,y=Predicted))+
                        geom_tile(aes(fill=prop*100))+
                        # scale_fill_viridis_c("%",limits=c(0,100),direction = -1)+
                        scale_fill_distiller("%",
                                             palette = "Oranges",
                                             limits=c(0,100),direction = 1)+
                        geom_text(aes(label=scales::percent(prop,1)))+
                theme_cowplot()+
                theme(axis.text.x = element_text(angle=45,hjust=1))+
                facet_wrap(.~markers)




two_test_data <-final_wide_nomissing %>%
                filter(cohort %in% c("HTI Vaccinee"))%>%
                mutate(`Full Set`=predict(two_fit_all,.),
                       `Three Markers`=predict(two_fit_three,.)
                       )         

two_test_data %>% 
        select(day,`Full Set`,`Three Markers`) %>%
        gather(Markers,prediction,-day) %>%
        group_by(day,Markers) %>%
        summarize(
                  `Recently Infected`=mean(prediction=="RecentlyInfected"),
                  `Not Recently Infected`=mean(prediction=="NotRecentlyInfected")
                  ) %>%
        gather(category,proportion,-c(day,Markers)) %>%
        ggplot(aes(x=factor(day),y=proportion))+
        geom_col(aes(fill=Markers),position=position_dodge2())+
        facet_wrap(.~category)




```


```{r etec}


final_df %>% filter(cohort %in% c("ETEC Challenge","SMIC/PIC")) %>%
        filter(day<50) %>%
        filter(status=="Case" | is.na(status))%>%
        filter(antigen_pretty %in% c("CT-B","Ogawa OSP")) %>%
        ggplot(aes(x=factor(day),y=RAU_value,col=cohort)
               )+
        geom_line(aes(group=id),  alpha=0.5)+
        facet_grid(antigen_pretty~isotype)+
        theme_cowplot()


etec_pred <-final_wide %>%
                filter(cohort %in% c("ETEC Challenge"))%>%
                mutate(
                       `Three Markers`=predict(two_fit_three,.)
                       )       




etec_pred %>% 
        ggplot(aes(y=id,x=factor(day)))+
        geom_tile(aes(fill=`Three Markers`))


```



Current figure 4 is everything below

```{r}


multi_class_data <- final_df %>%
        filter(status %in% c("Vaccinee","Case","Contact") ) %>%
        # filter(cohort %in% c("BGD Vaccinee","SMIC/PIC")) %>%
        #limit vaccinees to only baseline and "recent samples"
        # filter(!(status=="Vaccinee" & !(day>3  & day <45))) %>%
        mutate(vaxinf_class =case_when(
                status=="Case" & day > 3 & day<200 ~ "Recently Infected",
                status=="Vaccinee" & day> 3 & day<200 ~ "Recently Vaccinated",
                TRUE ~ "Neither"
        )) %>%
        left_join(antigen_df) 


var_list <- multi_class_data %>% distinct(marker) %>%
                filter(str_detect(marker,"CtxB|Ogawa|Inaba|TcpA|IgG_O139")) %>%
                unlist() %>% c("age") %>% as.character()


caret_data <- multi_class_data %>%
        select(cohort,sample,id,vaxinf_class,isotype,antigen_pretty,marker,RAU_value,day,age,status) %>% 
        filter(marker %in% var_list) %>%
                        select(-isotype,-antigen_pretty) %>%
                        mutate(RAU_value=log10(1/RAU_value)) %>%
                        spread(marker,RAU_value) %>%
                        mutate(vaxinf_class=str_remove_all(vaxinf_class," |,")) %>%
                        mutate(vaxinf_class=factor(vaxinf_class))




formula_all <- make_formula("vaxinf_class",var_list)
fit_all <- runCaretLOOCV(formula_all, dat=caret_data_nomissing)
importance_all <- caret::varImp(fit_all,scale=FALSE)

write_rds(fit_all,"source/final_code/vax_strategy/generated_rds/fit_all.rds")
write_rds(importance_all,"source/final_code/vax_strategy/generated_rds/importance_all.rds")
```


```{r}

fit_all <- read_rds("source/final_code/vax_strategy/generated_rds/fit_all.rds")
importance_all <- read_rds("source/final_code/vax_strategy/generated_rds/importance_all.rds")



proportion_15 <- caret_data_nomissing %>% 
        mutate(rowIndex=1:n()) %>%
        left_join(fit_all$pred)

roc_df15 <- proportion_15 %>%
        select(obs,RecentlyInfected,RecentlyVaccinated)  %>%
        gather(Class,value,-obs) %>%
        mutate(truth=ifelse(obs==Class,1,0))


#show roc curves and variable importance
roc_curve <- roc_df15 %>%
        mutate(Class = str_replace(Class,"Recently","Recently ")) %>%
        ggplot()+ 
        geom_roc(aes(m = value, d = truth,col=Class),labels=FALSE,n.cuts=0)+ 
        geom_abline(lty=2,col="grey50")+
        xlab("False Positivity Rate")+
        ylab("True Positivity Rate")+
        scale_color_manual(values=c("red","darkblue"))+
        theme_cowplot()+
        theme(legend.position = "none")


importance_plot <- importance_all$importance %>%
        mutate(Antibody=rownames(.)) %>%
        # left_join(distinct(multi_class_data,marker,
        #                    isotype,antigen,antigen_pretty)) %>%
        # mutate(Antibody=glue::glue("anti-{antigen_pretty} {isotype}")) %>%
        # slice_max(Overall,n=10)%>%
        ggplot(aes(x=Overall,y=reorder(Antibody,Overall)))+
                geom_col()+
        # scale_x_continuous("Gini Index",breaks=c(0,15,30),limits = c(0,30))+
        theme_bw()+
        theme(legend.position = "none",
              panel.grid=element_blank(),
              axis.title.y = element_blank()
             )


# model_plot<- ggdraw() +
#         draw_plot(roc_curve) +
        # draw_plot(importance_plot, x = 0.45, y = 0.23, width = .5, height = .6)

# confusion matrix
confusion_plot <- proportion_15 %>%
                group_by(pred,obs) %>%
                count() %>%
                group_by(obs) %>%
                mutate(prop=n/sum(n))%>%
                mutate(Predicted = str_replace(pred,"Recently","Recently\n")) %>%
                mutate(Observed = str_replace(obs,"Recently","Recently\n")) %>%
                ggplot(aes(x=Observed,y=Predicted))+
                        geom_tile(aes(fill=prop*100))+
                        # scale_fill_viridis_c("%",limits=c(0,100),direction = -1)+
                        scale_fill_distiller("%",
                                             palette = "Oranges",
                                             limits=c(0,100),direction = 1)+
                        geom_text(aes(label=scales::percent(prop,1)))+
                theme_cowplot()+
                theme(axis.text.x = element_text(angle=45,hjust=1))



plot_grid(roc_curve,importance_plot,confusion_plot,labels=c("A","B","C"))



#Using all the data
#use a 200 day window
#unweighted model with age for now


#Conduct LOOCV
#show importance
#show the confusion matrix

#Using just the bangladeshi data

#Conduct LOOCV
#show importance
#show the confusion matrix

#apply bangladeshi model to haitian data

```


\pagebreak


### Figure 5





