---
date: "`r Sys.Date()`"
output: 
    html_document: 
        toc: true
        toc_float: true
params:
  batch_id: batch_id 
  merge_obj: merge_obj
  iso: iso
title: "Quality Control for `r params$batch_id`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message=FALSE,warning=FALSE, eval = FALSE,
                      fig.width = 10, fig.height = 8)

pacman::p_load(
        tidyverse,
        downloadthis
)

```

## Overview

- Plate ID: `r params$batch_id` 
- Date of Run: `r params$merge_obj$layout_extract$summary$description[2,2]`
- Technician Name: `r if(params$merge_obj$layout_extract$summary$version=="1.1") params$merge_obj$layout_extract$summary$description[1,4]`
- Plate Notes: `r params$merge_obj$layout_extract$summary$description[3,2]`

Isotype:

```{r eval=TRUE}
params$merge_obj$layout_extract$summary$antibody %>%
  select(isotype,subclass,wells) %>%
  flextable::flextable() %>%
  flextable::autofit()

```

Antigen:

```{r eval=TRUE}

if(params$merge_obj$layout_extract$summary$version=="1.0"){
        
        params$merge_obj$layout_extract$summary$antigen %>%
                select(antigen_name,coupling_date,lot_number,wells)%>%
                  flextable::flextable() %>%
                  flextable::autofit()
                        
}


if(params$merge_obj$layout_extract$summary$version=="1.1"){
        
        params$merge_obj$layout_extract$summary$antigen %>%
                select(antigen_name,BeadID,coupling_date,lot_number,wells)%>%
                  flextable::flextable() %>%
                  flextable::autofit()
        
}

```


## Bead Counts

### Heatmap

```{r eval=TRUE}
full_data <- params$merge_obj$extract_merge %>%
                mutate(location_number=str_extract(location,"[0-9]{1,2}"),
                       location_letter=str_extract(location,"[A-Z]{1,2}")
                       ) %>%
                mutate(location_number=as.numeric(location_number))


full_data %>%
  full_join(expand_grid(location_letter=LETTERS[1:16],
                        antigen_exponent=unique(full_data$antigen_exponent)
  )) %>%
  filter(!is.na(sample))%>% 
  ggplot(aes(x=location_number,
             y=location_letter),
  )+
  geom_tile(aes(fill=Count))+
  # facet_wrap(.~batch)+
  scale_fill_viridis_b(option="viridis",direction=-1,breaks=c(1,30,50,100,1000),
                       trans="sqrt",
                       limits=c(0,3000)#,
                       # guide = guide_legend(label.theme = element_text())
                       
  )+
  theme_bw()+
  facet_wrap(.~antigen_exponent)+
  scale_x_continuous("Number",limits=c(0,24),breaks = c(6,12,18,24))+
  scale_y_discrete("Letter",limits=LETTERS[1:16] %>% rev())



```


### Antigen-wells with low counts

```{r eval=TRUE}

tab1 <- full_data %>% filter(Count<50) %>%  
  group_by(sample,location) %>%
  summarize(`<50 Beads occurrences`=n(),
            `<30 Beads occurrences`=sum(Count<30),
            `0 Beads occurrences`=sum(Count==0)
  ) %>%
  arrange(-`<30 Beads occurrences`) 

tab1 %>%
  DT::datatable()

tab1 %>% download_this(
  output_name = paste0("low_bead_counts_",params$batch_id),
  output_extension = ".xlsx",
  button_label = "Download as xlsx",
  button_type = "warning",
  has_icon = TRUE,
  icon = "fa fa-save"
)

```


### Samples without replicates

After removing all measurements with fewer than 30 beads, some samples will not have replicates.

```{r}
tab2 <- full_data %>% 
  group_by(sample,antigen_exponent) %>%
  summarize(`# of observations with 30+ Beads`=sum(Count>30)) %>%
  filter(`# of observations with 30+ Beads`<=1)

tab2 %>% DT::datatable()

tab2 %>% download_this(
  output_name = paste0("obs_bead_counts_",batch_id),
  output_extension = ".xlsx",
  button_label = "Download as xlsx",
  button_type = "warning",
  has_icon = TRUE,
  icon = "fa fa-save"
)


```



## Coefficient of variation (CV)

### Positive controls with CV>20%

In the past, we have retested plates when when over half of the positive control dilutions had >=X antigens with a coefficient of variation (calculated from replicate MFI measurements) greater than 20%.

```{r}

cv_df1 <- control_MFI %>%
  filter(str_detect(Sample,"Hi O1 Pos|Hi O139 Pos|Typhi 6 1:100")) %>%
  group_by(Sample,antigen,dilution,isotype) %>%
  summarize(n=n(),
            mean=mean(Median),
            sd=sd(Median),
            cv=sd/mean
  ) %>%
  group_by(Sample,dilution,isotype) %>%
  summarize(antigens=n(),
            `CV >=20%` = sum(cv>0.2)
  ) %>%
  arrange(dilution)


cv_df1 %>%DT::datatable()

cv_df1 %>% download_this(
  output_name = paste0("cv_summary_",batch_id),
  output_extension = ".xlsx",
  button_label = "Download as xlsx",
  button_type = "warning",
  has_icon = TRUE,
  icon = "fa fa-save"
)

```

### CV distribution among samples

```{r}

cv_df2 <- MFI_df %>% 
  group_by(Sample,antigen,isotype) %>%
  summarize(n=n(),
            mean=mean(Median),
            sd=sd(Median),
            cv=sd/mean
  )  %>%
  mutate(mean=signif(mean,3),
         sd=signif(sd,3),
         cv=signif(cv,3),
  ) %>%
  filter(n>1) %>%
  arrange(-cv)

cv_df2 %>% DT::datatable()
```

Dashed line is at CV of 20%.

```{r}
cv_df2 %>% ggplot(aes(x=cv))+
  geom_histogram(aes(fill=isotype))+
  theme_bw()+
  facet_wrap(.~antigen)+
  geom_vline(xintercept=0.2,lty=2,col="black")


```



## Dilution curve

- Dots indicate the log10(MFI) of dilutions on the curve
- Blue rugplot on left indicates the values of non-control wells
- Colored rugplot on the right indicate the log10(MFI) values of control wells

```{r}

# iso <- "IgA"

control_MFI %>%
  filter(isotype==iso,!is.na(dilution)) %>%
  mutate(std_type=case_when(str_detect(Sample,"O1 Standard") ~ "VC O1",
                            str_detect(Sample,"COVID") ~ "COVID",
                            str_detect(Sample,"Typhi") ~ "Typhi 6"
  )) %>%
  ggplot()+
  geom_point(aes(x=log10(dilution),y=log10(Median),pch=std_type),alpha=0.3)+
  geom_rug(data=control_MFI %>%
             filter(is.na(dilution)) %>%
             filter(isotype==iso),
           sides="right",
           aes(y=log10(Median),
               col=Sample
           ))+
  geom_rug(data=sample_MFI,
           sides="left",
           aes(y=log10(Median),
           ),alpha=0.3, col="blue")+
  facet_wrap(.~antigen)+
  theme_cowplot()+
  ylab("log10(MFI)")+
  ggtitle(paste(iso,"Dilution Series"))


```



## Full Data

### Luminex Data

```{r}

fd <- full_data %>% 
  select(location,isotype,antigen,Lot=lot_number,Sample,MFI=Median,Count) 

fd %>%
  DT::datatable()

fd %>%
  download_this(
    output_name = paste0("full_data_",batch_id),
    output_extension = ".xlsx",
    button_label = "Download as xlsx",
    button_type = "warning",
    has_icon = TRUE,
    icon = "fa fa-save"
  )
```

### Layout File

```{r}
layout_1 %>% gather(Number,Description,-Letter) %>%
  mutate(Location=paste0(Letter,Number)) %>% 
  filter(!is.na(Description)) %>%
  select(Location,Description) %>%
  DT::datatable()


```
